### 2015-03-26 tex/definitions.tex
Cleaned up the reference-equals proof, as well as miscellaneous other problems in proofs.tex. Commented out problems in Definitions.tex

\begin{definition}
\label{def:homomorphism}
A \textbf{homomorphism} $s_p \rightharpoonup_{h} s_q$, from state $s_p = ( \cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$ to state $s_q = ( \cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$, is defined as follows: 
$$
\begin{array}{l}
 s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
\end{array}
$$
\begin{comment}
$$
\begin{array}{l}
s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathit{fields}(\mathrm{type}(\cfgnt{l}_\beta))\ ( \\
\ \ \ \ \ \ \ \ \ \ \ \ \forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f ))\ ( \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists \phi_\beta\ ((\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f )))))))\\
\end{array}
$$
\end{comment}
\end{definition}

@@

\begin{lemma}[$Q$ is a singleton for $P \sqsubset Q$]
\label{lem:unique}
$$
P \sqsubset Q \Rightarrow \forall q,q^\prime \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \sqsubset q^\prime)
$$
The notation $P \sqsubset q$ is used to indicate that single member of
the set in the represented relation.
\end{lemma}
\begin{proof}
Please write me?
\end{proof}
\begin{definition}
\label{def:meta}
A state relation $p \rightarrow_x p^\prime$ is extended to sets of states $P \hookrightarrow_x P^\prime$ as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
The $\rgse$ relation over sets of states is $\rsgse = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FA(N)} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{FW(N)} \cup \hookrightarrow_\mathit{EQ(T)} \cup \hookrightarrow_\mathit{EQ(F)} \cup \hookrightarrow_\com$.%, and 
%the $\rsym$ relation extended to sets of states is 
%$$
%\rssym = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{EQ}^T \cup \hookrightarrow_\mathit{EQ}^F \cup \hookrightarrow_\com
%$$
\end{definition}

\begin{lemma}[$P$ and $Q$ have same number of successors when $P \sqsubset q$]
\label{lem:succCount}
Let $X = \{P^\prime | P \leadsto P^\prime\}$ and $Y = \{q^\prime | q
\rsym q^\prime\}$: $P \sqsubset q \Rightarrow |X| = |Y|$.
\end{lemma}
\begin{proof}
Please write me?
\end{proof}

@@

Note that in the literature it is customary to define bisimulation in
terms of a single labeled transition system, whereas for the purposes
of this paper the definition of bisimulation refers to a pair of
transition relations $\rightarrow_x$ and $\rightarrow_y$ defined by
reduction rules. Since it is possible to create a union of the two
rule systems $\rightarrow_x \cup \rightarrow_y$, and since none of the
transitions in the reduction rules in this paper are labeled, this
definition is sufficient for all of the customary properties of
bisimulation to apply. For a more detailed treatment on the
application of bisimulation to reduction rule systems see
\cite{GSE:barbedbisimulation}.

>>>>

\begin{definition}
\label{def:homomorphism}
A \textbf{homomorphism} $s_p \rightharpoonup_{h} s_q$, from state $s_p = ( \cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$ to state $s_q = ( \cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$, is defined as follows: 
$$
\begin{array}{l}
 s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\alpha\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathcal{F}( \exists \phi_\alpha\ (\exists \phi_\beta\ ( \\ 
\ \ \ \ \ \ \ \ \ \ \ \ (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f )) \Rightarrow \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  (\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f ))\ \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  )) ) ) ) )
\end{array}
$$
\begin{comment}
$$
\begin{array}{l}
s_p \rightharpoonup_{h} s_q \Leftrightarrow \\
\ \ \ \ \exists h: \mathcal{L} \mapsto \mathcal{L}\ (\forall \cfgnt{l}_\beta\ (\forall f \in \mathit{fields}(\mathrm{type}(\cfgnt{l}_\beta))\ ( \\
\ \ \ \ \ \ \ \ \ \ \ \ \forall (\phi_\alpha\ \cfgnt{l}_\alpha) \in \cfgnt{L}_p(\cfgnt{R}_p (\cfgnt{l}_\beta,f ))\ ( \\
\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \exists \phi_\beta\ ((\phi_\beta\ h(\cfgnt{l}_\alpha))\in \cfgnt{L}_q(\cfgnt{R}_q (h(\cfgnt{l}_\beta),f )))))))\\
\end{array}
$$
\end{comment}
\end{definition}

@@

%\begin{lemma}[$Q$ is a singleton for $P \sqsubset Q$]
%\label{lem:unique}
%$$
%P \sqsubset Q \Rightarrow \forall q,q^\prime \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \sqsubset q^\prime)
%$$
%The notation $P \sqsubset q$ is used to indicate that single member of
%the set in the represented relation.
%\end{lemma}
%\begin{proof}
%Please write me?
%\end{proof}

\begin{definition}
\label{def:meta}
A state relation $p \rightarrow_x p^\prime$ is extended to sets of states $P \hookrightarrow_x P^\prime$ as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p \in P\ (\forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime))
$$
The $\rgse$ relation over sets of states is $\rsgse = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FA(N)} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{FW(N)} \cup \hookrightarrow_\mathit{EQ(T)} \cup \hookrightarrow_\mathit{EQ(F)} \cup \hookrightarrow_\com$.%, and 
%the $\rsym$ relation extended to sets of states is 
%$$
%\rssym = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{EQ}^T \cup \hookrightarrow_\mathit{EQ}^F \cup \hookrightarrow_\com
%$$
\end{definition}

%\begin{lemma}[$P$ and $Q$ have same number of successors when $P \sqsubset q$]
%\label{lem:succCount}
%Let $X = \{P^\prime | P \leadsto P^\prime\}$ and $Y = \{q^\prime | q
%\rsym q^\prime\}$: $P \sqsubset q \Rightarrow |X| = |Y|$.
%\end{lemma}
%\begin{proof}
%Please write me?
%\end{proof}

@@

Note that in the literature it is customary to define bisimulation in
terms of a single labeled transition system, whereas for the purposes
of this paper the definition of bisimulation refers to a pair of
transition relations $\rightarrow_x$ and $\rightarrow_y$ defined by
reduction rules. Since it is possible to create a union of the two
rule systems $\rightarrow_x \cup \rightarrow_y$, and since none of the
transitions in the reduction rules in this paper are labeled, this
definition is sufficient for all of the customary properties of
bisimulation to apply. 
%For a more detailed treatment on the
%application of bisimulation to reduction rule systems see
%\cite{GSE:barbedbisimulation}.
